Universal Anonymous Signatures

### 2022-04-19 prism-backend/research/gsac/construction-uas.tex
First draft of forge-issue proof. Working on forge-sign. Refined properties.

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\upk,\scred,\attrs)\rangle$.} %
The protocol is run between an issuer, and a user with secret key \usk and
credentials \scred, where each $\cred \in \scred$ is issued by an issuer with
public key $\ipk_{\cred}$ (which we assume that the user can easily retrieve,
e.g., from secure storage, given \cred), and attests attributes
$\attrs_{\cred}$. The user
requests a signature on a commitment to the user key, as well as on the
attributes in \attrs. In addition, the user proves that the issuance function
\fissue established by the issuer is satisfied by the credentials in $\scred$
and its user secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace
(\usk,\scred), (\Ccom,\attrs): \Ccom = \CCommit(usk) \land \fissue(\usk,\scred,
\attrs) = 1 \land \forall \cred \in \scred, \SBCMVerify(\ipk_{\cred},\cred,
\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1 \rbrace$. The interactive protocol
for a user to obtain a credential from an issuer of the system is as follows:

\begin{itemize}
\item \uline{User}: Commit to the user secret key with $\Ccom \gets
  \CCommit(\usk)$. Compute proof $\NIZKproof \gets
  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred),(\Ccom,
  \attrs))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
  (\NIZKcrs_{\Issue},\NIZKproof,(\Ccom,\attrs))$, and abort if it fails. Then,
  compute the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,
  \attrs)$. Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\cred,
  \NIZKproof)$.
\item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
  \attrs \cup \lbrace \usk \rbrace)$. Reject if verification fails.
  Otherwise, return \cred.
\end{itemize}

\paragraph{$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
In the signing algorithm, we make use of the following relation:
$\NIZKRel_{\Sign} = \lbrace (\usk,\scred,\yinsp),(\msg,\feval,\yeval,\Ec,\sipk)
: \Ec = \EEnc(\Eek,\yinsp) \land \yeval = \feval(\usk,\scred,\msg) \land
\yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1)
\rbrace$ where, for each $\cred \in \scred$, $\attrs_{\cred}$ and $\ipk_{\cred}$
are as in $\langle \Obtain,\Issue \rangle$.
%
From this, in order to produce a valid signature, the user first evaluates
$\yeval \gets \feval (\usk,\scred,\msg)$, and decides whether or not to continue
with the signing process -- this may depend, e.g., on the inspection policy of
\opk, as the output of \feval may influence whether the user will be
de-anonymizable or not, depending on the \finsp function in \opk.
%
Then, the user parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
compute $\yinsp \gets \finsp(\yeval,\usk,\scred,\msg)$, and encrypt it with
\Eek by running $\Ec \gets \EEnc(\Eek,\yeval)$. Finally, the user computes
$\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
\yinsp),(\msg,\feval,\yeval,\Ec,\sipk))$ and  outputs $(\sig = (\NIZKproof,\Ec),
\yeval)$.

>>>>

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\upk,\sipk,\attrs)\rangle$.} %
The protocol is run between an issuer, and a user with secret key \usk and
credentials \scred, where each $\cred \in \scred$ is issued by an issuer with
public key $\ipk_{\cred}$ (which we assume that the user can easily retrieve,
e.g., from secure storage, given \cred), and attests attributes
$\attrs_{\cred}$. For readability we write $\attrs_{\scred}$ as abbreviation for
$\lbrace \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for
$\sipk_{\scred}$. The user requests a signature on a commitment to the user key,
as well as on the attributes in \attrs. In addition, the user proves that the
issuance function \fissue established by the issuer is satisfied by the
credentials in $\scred$
and its user secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace
(\usk,\scred,\attrs_{\scred}), (\Ccom,\attrs,\sipk_{\scred}): \Ccom = \CCommit(usk) \land
\fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,
\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1 \rbrace$. The interactive protocol
for a user to obtain a credential from an issuer of the system is as follows:

\begin{itemize}
\item \uline{User}: Commit to the user secret key with $\Ccom \gets
  \CCommit(\usk)$. Compute proof $\NIZKproof \gets
  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred,\attrs_{\scred}),
  (\Ccom,\attrs))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
  (\NIZKcrs_{\Issue},\NIZKproof,(\Ccom,\attrs,\sipk))$, and abort if it fails. Then,
  compute the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,
  \attrs)$. Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\sipk,
  \cred,\NIZKproof)$.
\item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
  \attrs \cup \lbrace \usk \rbrace)$. Reject if verification fails.
  Otherwise, return \cred.
\end{itemize}

\paragraph{$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
In the signing algorithm, we make use of the following relation:
$\NIZKRel_{\Sign} = \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r),(\msg,\feval,
\yeval,\Ec,\sipk_{\scred},\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land \yeval =
\feval(\usk,\scred,\msg) \land
\yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1)
\rbrace$ where, for each $\cred \in \scred$, $\attrs_{\cred}$ and $\ipk_{\cred}$,
as well as $\attrs_{\scred}$ and $\sipk_{\scred}$ are as in $\langle \Obtain,
\Issue \rangle$.
%
From this, in order to produce a valid signature, the user first evaluates
$\yeval \gets \feval (\usk,\scred,\msg)$, and decides whether or not to continue
with the signing process -- this may depend, e.g., on the inspection policy of
\opk, as the output of \feval may influence whether the user will be
de-anonymizable or not, depending on the \finsp function in \opk.
%
Then, the user parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
compute $\yinsp \gets \finsp(\yeval,\usk,\scred,\msg)$, and encrypt it with
\Eek by running $\Ec \gets \EEnc(\Eek,\yeval;r)$ for some fresh randomness $r$.
Finally, the user computes
$\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
\attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek))$ and
outputs $(\sig = (\NIZKproof,\Ec),\yeval)$.

### 2022-04-19 prism-backend/research/gsac/model-uas.tex
First draft of forge-issue proof. Working on forge-sign. Refined properties.

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
  its inspecting key pair. The function \finsp defines the type of utility that
  will be extractable from those pairs that do not meet conditions defined
  at signing time (typically, by verifiers).
\item[$\usk \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\lbrace (\cred_i,\ipk_i)\rbrace_{i \in \Issuers},\attrs),
  \Issue(\isk,\lbrace \ipk_i \rbrace_{i \in \Issuers},\attrs))
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of $(\cred_i,\ipk_i)$ pairs,
  where $\cred_i$ is a credential obtained from the issuer with public
  key $\ipk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the group to which each
  credential belongs is available from the credential itself, and therefore
  omit the $\ipk_i$ values from the syntax, unless necessary to avoid ambiguity.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
  \rbrace_{i \in \Issuers},\msg,\feval)$.] %
  Upon receiving a user secret key \usk, inspector public key \opk, a set of
  credential-issuer pairs $(\cred_i,\ipk_i)$, a message \msg and evaluation
  function \feval, returns signature \sig and value \yeval.
\item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
  \yeval,\msg,\feval)$.] Checks whether $(\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys $\ipk_i$, for evaluation function \feval and inspector key \opk.
\item[$(\yinsp,\iproof)/\bot \gets \Inspect(\osk,\lbrace \ipk_i
  \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
  Executed by the inspector with private key \osk. Receives a signature $(\sig,
  \yeval)$ over message \msg and evaluation function \feval, generated using
  credentials issued by the issuers with public keys $\ipk_i$. If \sig is valid,
  the function outputs a value $\yinsp$ derived from the signer's public key,
  credentials, message, and signature, as well as a proof of correct
  inspection.
\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\yinsp,
  \iproof,\sig,\yeval,\msg,\feval)$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \yinsp,
  obtained by applying \Inspect to the the signature $(\sig,\yeval)$ over
  message \msg, and for evaluation function \feval. 
\end{description}

@@

\paragraph{Helper functions \ExtractIssue and \ExtractSign.} In our modelling,
we assume the existence of two functions, \ExtractIssue and \ExtractSign. They
are not functions available in the actual scheme, but rather to the challenger,
in the experiments we use to formalize security fof \UAS. Indeed, similar
techniques have been used before to prove security in privacy-preserving schemes
with some sort of accountability, but that do not offer conventional opening as
vanilla group signatures. For instance, see related works on DAA
\cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}
More concretely, both functions are as follows:

\begin{description}
\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\scred)$.] Receives an
$\langle \Obtain, \Issue \rangle$ transcript, and returns the credentials (if
any) and user secret key used during the execution of the protocol. It clearly
needs an honest issuer as, otherwise, the transcripts won't be available.
Consequently, we only use it to define the properties that require an honest
issuer.
\item[$\ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,\scred)$.]
Receives a signature pair $(\sig,\yeval)$, as well as the inspector identifier
\oid, and the identifiers of all issuers of the credentials used to produce the
signature over \msg, and for \feval. It outputs the user secret key
and credentials used to generate the signature.
\end{description}

Note that, both for \ExtractIssue and \ExtractSign, in the case of transcripts
and signatures by honest users, it is enough to have access to the corresponding
state information (described below) maintained by the challenger in our
experiments. For join transcripts of corrupt users, or dishonestly produced
signatures, we do need to perform actual extraction. How to do this will depend
on each specific construction. Certainly, the challenger needs special
knowledge/power such as decryption trapdoors, the ability to rewind the game, or
program random oracles; the approach needs thus to depend on the concrete
construction. Although, for the case of \ExtractIssue, online extractability
(or alternative requirements, such as non-parallel or logarithmic number of
joins) is necessary. \todo{\needcite Paper from Camenisch and Shoup on the need
  for online extractability?} \todo{How do we do this in our construction(s)?
  Can we be more specific here? Also, this poses an interesting question: Is
  extraction a requirement for this kind of schemes? Can we find alternative
  definitions?}

@@

% \paragraph{Extractability.} %
% \commentwho{Jesus}{I have a doubt here. On one hand, modelling the
%   extractability-related properties here as in \cite{lnpy21} would lead to
%   redundancy with the current unforgeability properties. I do like the
%   precission in the definition of \cite{lnpy21}; but I do not like that,
%   within the extractability property, they include ``domain-specific''
%   concepts (e.g., open, etc.) On the other hand, we could model extractability
%   as (an extension of) the Identify approach in e.g. \cite{gl19,dl21}. What
%   I like about that is that it would not be redundant (we just assume the
%   existance of a function extracting some secret values). What I do not like,
%   is that the definition is not as precise as in \cite{lnpy12}. Namely, at the
%   design stage, one just has to informally describe what Identify-Extract does;
%   then, what it *really* does, has to be defined in the security proofs. That
%   is, its definition is somehow deferred, which makes the presentation a bit
%   harder to follow, IMO.}

% Before getting into the ``actual'' security properties, we introduce an
% auxiliary yet crucial property, extractability, that will allow us to formally
% define unforgeability-related properties in a meaningful way. More concretely,
% we require issuance extractability, and signing extractability. Informally, with
% issuance extractability we require that given an additional trapdoor generated
% at setup time, it is possible to extract the witnesses (user secret key and
% credentials) used to request issuance of a new credential, from its $\langle
% \Obtain,\Issue \rangle$ transcript. With signing extractability, we refer to the
% requirement to be able to extract, given an additional trapdoor, the user secret
% key and credentials used to produce any (possibly maliciously generated)
% signature. The need to differentiate both comes from the fact that, for issuance
% extractability, we need to assume honest issuers -- as otherwise, the $\langle
% \Obtain,\Issue\rangle$ transcripts may
% just not exist. Other than that, both properties are essentially the same: given
% some proof an instance of an NP relation, they allow extracting the
% corresponding witnesses. The need to resort to this extraction technique comes
% from the fact of not including a conventional opening functionality. Indeed,
% this has been used (at times, somehow implicitly) in related works on DAA
% \cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}.

% In more detail, we require the existence of three additional algorithms,
% \ExtractSetup, \ExtractIssue, and \ExtractSign, as follows:

% \begin{description}
% \item[$\ExtractSetup(1^\secpar) \rightarrow (\parm,\extracttrap)$.] \todo{Describe,
%     and mention that it must be indistinguishable from \Setup.}
% \item[$\ExtractIssue(\extracttrap,\utrans) \rightarrow (\usk,\scred)$.] \todo{Describe.}
% \item[$\ExtractSign(\extracttrap,\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,\scred)$.]
%   \todo{Describe.}
% \end{description}

% With these algorithms, we formally define the issuance extractability and
% signing extractability properties as shown in \figref{fig:exp-uas-extract}.

% \begin{figure}[htp!]
%   \procedure{$\ExpExtractIssue(\utrans)$}{%
%     \pcreturn (\usk,\scred) \\    
%   }

%   \procedure{$\ExpExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
%     \pcreturn (\usk,\scred)
%   }

%   \caption{Issuance and signing extractability experiments for \UAS schemes.}
%   \label{fig:exp-uas-extract}
% \end{figure}

% \begin{definition}{(Extractable issuance of \UAS)}
%   We define the advantage \AdvExtractIssue of $\adv$ against \ExpExtractIssue as
%   $\AdvExtractIssue=\Pr\lbrack\ExpExtractIssue(1^\secpar)=1\rbrack$.
%   %
%   A \UAS scheme has extractable issuance if, for any p.p.t. adversary $\adv$,
%   \AdvExtractIssue is a negligible function of $1^\secpar$.
% \end{definition}

% \begin{definition}{(Extractable signing of \UAS)}
%   We define the advantage \AdvExtractSign of $\adv$ against \ExpExtractSign as
%   $\AdvExtractSign=\Pr\lbrack\ExpExtractSign(1^\secpar)=1\rbrack$.
%   %
%   A \UAS scheme has extractable signing if, for any p.p.t. adversary $\adv$,
%   \AdvExtractSign is a negligible function of $1^\secpar$.
% \end{definition}

% For short, we say that an \UAS scheme that has both extractable issuance and
% signing, is an extractable \UAS scheme.

@@

\begin{figure}[htp!]
    \procedure{$\ExpForgeIssue(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      \cid \gets \adv^{\Oforgeissue}(\parm) \\
      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
      w \gets \ExtractIssue(\trans[\cid]) \\
      \pcif w = \bot: \pcreturn 1 \\
      \textrm{Parse}~w~\textrm{as}~(\usk,\lbrace (\cred_i,\ipk_i)
      \rbrace_{i \in \Issuers})  \\      
      \pcif \fissue(\usk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
      \ATTR[\cid]) = 0: \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
  \label{fig:exp-uas-unfor-issue}
\end{figure}

\begin{figure}[htp!]
    \procedure{$\ExpForgeSign(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\oid,\siid,\sig,\yeval,\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
      \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\yeval,\msg,\feval) = 0:
      \pcreturn 0 \\
      (\yinsp,\iproof) \gets \Inspect(\PRVOK[\oid],\siid,\sig,\yeval,\msg) \\
      \pcif \yinsp = \bot \lor \iproof = \bot \lor       
      \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg,\feval)
      = 0: \pcreturn 0 \\
      (\usk,\scred) \gets \ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \\
      \pcif \feval(\usk,\scred,\msg) \neq \yeval: \pcreturn 1 \\
      \pcif \finsp(\yeval,\usk,\scred,\msg) \neq \yinsp: \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
  \label{fig:exp-uas-unfor-sign}
\end{figure}

>>>>

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
  its inspecting key pair. The function \finsp defines the type of utility that
  will be extractable from those pairs that do not meet conditions defined
  at signing time (typically, by verifiers).
\item[$\usk \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\lbrace (\cred_i,\ipk_i)\rbrace_{i \in \Issuers},\attrs),
  \Issue(\isk,\lbrace \ipk_i \rbrace_{i \in \Issuers},\attrs))
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of $(\cred_i,\ipk_i)$ pairs,
  where $\cred_i$ is a credential obtained from the issuer with public
  key $\ipk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the group to which each
  credential belongs is available from the credential itself, and therefore
  omit the $\ipk_i$ values from the syntax, unless necessary to avoid ambiguity.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
  \rbrace_{i \in \Issuers},\msg,\feval)$.] %
  Upon receiving a user secret key \usk, inspector public key \opk, a set of
  credential-issuer pairs $(\cred_i,\ipk_i)$, a message \msg and evaluation
  function \feval, returns signature \sig and value \yeval.
\item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
  \yeval,\msg,\feval)$.] Checks whether $(\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys $\ipk_i$, for evaluation function \feval and inspector key \opk.
\item[$(\yinsp,\iproof)/\bot \gets \Inspect(\osk,\lbrace \ipk_i
  \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
  Executed by the inspector with private key \osk. Receives a signature $(\sig,
  \yeval)$ over message \msg and evaluation function \feval, generated using
  credentials issued by the issuers with public keys $\ipk_i$. If \sig is valid,
  the function outputs a value $\yinsp$ derived from the signer's public key,
  credentials, message, and signature, as well as a proof of correct
  inspection.
\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\yinsp,
  \iproof,\sig,\yeval,\msg,\feval)$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \yinsp,
  obtained by applying \Inspect to the the signature $(\sig,\yeval)$ over
  message \msg, and for evaluation function \feval. 
\end{description}

@@

\paragraph{Helper functions \ExtractIssue and \ExtractSign.} In our modelling,
we assume the existence of three functions, \Identify, \ExtractIssue and
\ExtractSign. They are not functions available in the actual scheme, but rather
to the challenger, in the experiments we use to formalize security fof \UAS.
Indeed, similar techniques have been used before to prove security in
privacy-preserving schemes with some sort of accountability, but that do not
offer conventional opening as vanilla group signatures. For instance, see
related works on DAA \cite{bfg+11,cdl16} and group signature variants
\cite{dl21,fgl21,gl19,lnpy21}. More concretely, both functions are as follows:

\begin{description}
\item[$\Identify(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
  Otherwise, it returns $0$.
\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\scred,\attrs_{\scred})$.]
  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
  credentials (if any), their attributes, and the user secret key used during
  the execution of the $\langle\Obtain,\Issue\rangle$ protocol. It clearly needs
  an honest issuer as, otherwise, the transcripts won't be available.
  Consequently, we only use it to define the properties that require an honest
  issuer.
\item[$\ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,\scred)$.]
  Receives a signature pair $(\sig,\yeval)$, as well as the inspector identifier
  \oid, and the identifiers of all issuers of the credentials used to produce the
  signature over \msg, and for \feval. It outputs the user secret key
  and credentials used to generate the signature.
\end{description}

Note that, both for the three functions, in the case of credentials,
transcripts, and signatures by honest users, it is enough to have access to the
corresponding state information (described below) maintained by the challenger
in our experiments. For credentials and join transcripts of corrupt users, or
dishonestly produced signatures, we do need to perform actual extraction. How to
do this will depend on each specific construction. Certainly, the challenger
needs special knowledge/power such as decryption trapdoors, the ability to
rewind the game, or program random oracles; the approach needs thus to depend on
the concrete construction. Although, for the case of \ExtractIssue, online
extractability (or alternative requirements, such as non-parallel or logarithmic
number of joins) is necessary. %
\todo{\needcite Paper from Camenisch and Shoup on the need
  for online extractability?} \todo{How do we do this in our construction(s)?
  Can we be more specific here? Also, this poses an interesting question: Is
  extraction a requirement for this kind of schemes? Can we find alternative
  definitions?}

@@

@@

\begin{figure}[htp!]
    \procedure{$\ExpForgeIssue(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      \cid \gets \adv^{\Oforgeissue}(\parm) \\
      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trans[\cid]) \\
      \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
      \exists \cred \in \scred~\st~\Identify(\usk,\attrs_{\cred},\cred) = 0: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
  \label{fig:exp-uas-unfor-issue}
\end{figure}

\begin{figure}[htp!]
    \procedure{$\ExpForgeSign(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\oid,\siid,\sig,\yeval,\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
      \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\yeval,\msg,\feval) = 0:
      \pcreturn 0 \\
      (\yinsp,\iproof) \gets \Inspect(\PRVOK[\oid],\siid,\sig,\yeval,\msg) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg,\feval)
      = 0: \pcreturn 0 \\
      (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets \ExtractSign(\oid,\siid,\sig,
      \yeval,\msg,\feval) \\
      \pcif \feval(\usk,\scred,\msg) \neq \yeval: \pcreturn 1 \\
      \pcif \finsp(\yeval,\usk,\scred,\msg) \neq \yinsp \lor \yinsp \neq \yinsp':
      \pcreturn 1 \\
      \pcif \exists \cred \in \scred~\st~\Identify(\usk,\attrs_{\cred},\cred) = 0:
      \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
  \label{fig:exp-uas-unfor-sign}
\end{figure}
